---
title: "Wharton Accounting -- Homework 1"
author: "Joe Nguyen"
date: "5 January 2016"
output: html_document
---

```{r, echo=FALSE}
rm(list = ls())

# Change working directory
dirBase <- "/home/joe/Documents/01-coursera/02-finance"
dirWorking <- "/accounting-wharton"
setwd(paste0(dirBase, dirWorking))

# Generic finance functions
source(paste0(dirBase, "/01-tvm/r-code/func_finance.R"))
```


### Question 1
Which of the following is a required financial statement?  
**Statement of Cash Flows**

All statements are:

- Balance Sheet
- Income Statement
- Statement of Cash Flows
- Statement of Stockholders' Equity


### Question 2
Which of the following items reduce Net income?

**Expenses** since:
$$
\text{Net Income} = \text{Revenue} - \text{Expenses}
$$


### Question 3
What are Revenues in the table below?  

| Item | Value |
| --- | --- |
| Total Assets |	300 |
| Total Liabilities | 	160 |
| **Total Stockholders' Equity** |	 |
| Beginning Retained Earnings| 	50 |
| Ending Retained Earnings| 	60 |
| Dividends| 	15 |
| Revenues| 	? |
| Expenses| 	100 |
| **Net Income** | 	 |
| Cash| 	30 |

$$
\begin{align}
\text{Assets} = \text{Liabilities} &+ \text{Stockholders' Equity} \\
                                   &+ \left( \text{Contributed Capital} + \text{Retained Earnings} \right)
\end{align}
$$
$$
\begin{align}
\text{Retained Earnings} = \text{Prior Retained Earnings} &+ \text{Net Income} - \text{Dividends} \\
                                                          &+ \left( \text{Revenue} - \text{Expenses} \right)
\end{align}
$$

Rearranging for Revenues:  
$$
\text{Revenue} = \text{Assets} - \text{Liabilities} - \text{Contributed Capital} - \text{Prior Retained Earnings} + \text{Expenses} + \text{Dividends}
$$
```{r}
300 - 160 - 50 + 100 + 15
```

or just looking at **Stockholders' Equity**:  
$$
\text{Retained Earnings} = \text{Prior Retained Earnings} + \left( \text{Revenue} - \text{Expenses} \right) - \text{Dividends}
$$
$$
\text{Revenue} = \text{Retained Earnings} - \text{Prior Retained Earnings} + \text{Expenses} + \text{Dividends}
$$
```{r}
60 - 50 + 100 + 15
```


### Question 4
Which of the following transactions violate the balance sheet equation?  

- **Increase Retained Earnings and increase a Liability**
- **Reduce cash and reduce an expense**
- **Increase a liability and increase a revenue**
- **Increase an expense and reduce a liability**

NOTE: Cash is an asset (on LHS of equation).

#### Above incorrect, include:  
- **Increase cash and reduce contributed capital**


### Question 5
Which of the following are assets?

- **Cash**
- **Accounts Receivable** -- money owed to company by its debtors

| Other choices | Type |
| --- | --- |
| Accounts Payable | Liability |
| Retained Earnings | Equity |
| Common Stock | Equity |


### Question 6
Which of the following accounts would be increased with a Debit?  

- **Land** (asset)
- **Cash** (asset)
- **Advertising Expense** (expense)
- **Prepaid Insurance** (asset)

**Accounts Payable** (liability) decreases with a Debit.


### Question 7
Which of these journal entries represent paying cash to buy an asset?  

Dr. Truck 5000  
    Cr. Cash    5000

Dr. Prepaid Insurance     500  
    Cr. Cash                         500

Dr.  Advances from Customers    50  
    Cr.  Cash                                       50

#### Above incorrect, remove:  
Advances from Customers  


### Question 8
Which journal entry reflects the following transaction:  
BOC sold 10,000 shares of $1 par value stock to investors for $5 per share.

Dr. Cash    50,000  
    Cr. Common Stock                10,000  
    Cr. Additional Paid-in Capital  40,000  


### Question 9
Which journal entry reflects the following transaction:  
BOC bought $10,000 of inventory on account.

Dr. Inventory   10,000
    Cr. Cash        10,000

#### Above incorrect:  
No cash was paid, instead, CR Accounts Payable (+L)

Dr. Inventory   10,000  
    Cr. Accounts Payable (+L)        10,000
    

### Question 10
Which journal entry reflects the following transaction:  
BOC declared a $9,000 dividend to be paid in cash next month.

Dr. Retained Earnings (-SE)   9,000  
    Cr. Dividends Payable (+L)  9,000




