---
title: "Wharton Accounting -- Homework 3"
author: "Joe Nguyen"
date: "14 January 2016"
output: html_document
---

```{r, echo=FALSE}
rm(list = ls())

# Change working directory
dirBase <- "/home/joe/Documents/01-coursera/02-finance"
dirWorking <- "/accounting-wharton"
setwd(paste0(dirBase, dirWorking))

# Generic finance functions
source(paste0(dirBase, "/01-tvm/r-code/func_finance.R"))
```


### Question 1
Which of the following would be a cash flow from operating activities? (check all that apply)  

- **Amortisation of a patent**
- **Loss on sale of equipment**
- **Collections from customers**
- **Payments for salaries and wages**

Others:
- Purchases of equipment (Investing)

#### Above Incorrect, correct items:
- **Collections from customers**
- **Payments for salaries and wages**

Non-operating:
- Amortisation of a patent (noncash transaction)
- Loss on sale of equipment (investing)


### Question 2
Which of the following would be a cash flow from investing activities? (check all that apply)  

- **Payments to acquire a company**
- **Proceeds from selling equipment**

Others:
- Depreciation on a building (operating)
- Proceeds from issuing stock (financing)
- Purchases of inventory (operating)


### Question 3
A company has the following cash flows:

Cash from operations 10
Cash from investing activities (1)
Cash from financing activities (9)

Which growth stage best describes this pattern of cash flows?  
**Stable**

#### Above Incorrect, perhaps:
**Perky (lively)** lots of negative financing cash flow due to issuing of stocks

#### Above Incorrect, perhaps:
**Early growth** due to issuing of stocks (financing), since **Perky** is not a formal stage name


### Question 4
A company bought $50,000 of inventory for $20,000 cash, with the balance due to the supplier in 30 days. What is the operating cash flow in this transaction?  
**($20,000)**

You can think of this as two transactions. First, the company bought $20,000 of inventory with cash. This is an operating cash flow. Second, the company bought $30,000 of inventory on account. This is a non-cash transaction. So, the operating cash flow is ($20,000).


### Question 5
Which of the following would be shown as a **positive** number in the Operating section of the SCF under the indirect method? (check all that apply)  

For indirect method, subtract debits and add credits to keep cash neutral:
$$
\begin{align}
\text{Debits} &= \text{Credits} \\
\text{Cash} + \text{Non-cash Assets} &= \text{Liabilities} + \text{Owner's Equity}
\end{align}
$$

- **Depreciation on a building**
- **Increase in Income Taxes Payable**
- **Decrease in Inventory**

Negative:

- Proceeds from a mortgage
- Gain on sale of equipment


### Question 6
A company has Net Income of $20, which included $4 of depreciation expense. There were no other noncash expenses in Net Income and there were no gains or losses. Accounts receivable was $40 at the beginning of the year and $25 at the end of the year. Accounts Payable was $25 at the beginning of the year and $15 at the end of the year. Inventory was $22 at the beginning of the year and $27 at the end of the year. All other balance sheet accounts were unchanged over the year. What was the company’s Cash Flow from Operating Activities?

| Items | Indirect SCF |
| --- | --- | --- |
| Net Income | 20 |
| Depreciation Expenses | 4 |
| Change in Accounts Receivable | (25) - (40) = 15 |
| Change in Accounts Payable | 15 - 25 = (10) |
| Change in Inventory | (27) - (22) = (5) |
| **Net Cash from Operations** | **24** |


### Question 7
A company put together a preliminary version of its financial statements. Its Net Income was $200, its Depreciation Expense was $40, and its Cash Flow from Operations was $90. The accountant found an error in computing straight-line Depreciation Expense. It should have been $50. What is Cash from Operations after fixing this mistake? (you can ignore taxes)

```{r}
adjustments <- 90 - 200 - 40; adjustments
cash.operations <- 200 + 50 + adjustments; cash.operations
```


#### Above incorrect, answer:
**90**  
Net Income would drop by $10 with the extra expense. The amount of depreciation expense added back would go up by $10. These would cancel each other out and there would be no effect on Cash from Operations. So, Cash from Operations would remain at $90. 


### Question 8
A company sold PP&E for $100 cash. Prior to the sale, the net book value of the PP&E on the financial statements was $80. Thus, the company recorded a Gain on Sale of Equipment of $20 in Net Income. What is the investing cash flow in this transaction?
**$100** Proceed from sale of PPE on SCF  
"Gain of sale of PP: 20" goes on income statement


### Question 9
Which of the following transactions would result in the change in Inventory on the SCF being a different number than the change in Inventory on the Balance Sheet? (check all that apply)

- **Some of the inventory came in the acquisition of another company**
- **Some of the inventory was purchased on account**
- **Some of the inventory is held by subsidiaries in countries that use a different currency**

SCF Complications (Lecture Slides-3.3.1-more-scf-ebitda); corresponding categories for above items:

- Acquisitions and divestitures of businesses
- Noncash investing and financing activities
- Foreign Currency Translation Adjustments

Non-items:
- Some of the inventory was sold for cash
- Some of the inventory was stolen by employees


### Question 10
A company had EBITDA of $1000, Depreciation and Amortization Expense of $100, Interest Expense of $100, and Tax Expense of $50. What was the company’s Net Income?

| Net Income | 1,000 - 100 - 100 - 50 = **750** |
| --- | --- |
| Depreciation and Amortization Expense | 100 |
| Interest Expense | 100 | 
| Tax Expense | 50 |
| EBITDA | 1,000 |

