---
title: "Wharton Accounting -- Final Exam, Part 2"
author: "Joe Nguyen"
date: "24 January 2016"
output: html_document
---

```{r, echo=FALSE}
rm(list = ls())

# Change working directory
dirBase <- "/home/joe/Documents/01-coursera/02-finance"
dirWorking <- "/accounting-wharton"
setwd(paste0(dirBase, dirWorking))

# Generic finance functions
source(paste0(dirBase, "/01-tvm/r-code/func_finance.R"))
```


### Question 1
During the quarter ended 3/31/2015, Clarke Biscuits Inc. collected $100 of cash from customers, paid $60 of cash to suppliers, paid $20 of cash to employees and other creditors, and recorded $10 of depreciation expense. There were no other cash flows related to operating activities.

What was Clarke’s Cash Flow from Operations during the quarter ended 3/31/2015?

```{r}
customers <- 100
suppliers <- -60
employees <- -20
deprec <- -10

cf <- customers + suppliers + employees + deprec; cf
```

#### Incorrect
Should be **$20**, depreciation not included in operating CF.


### Question 2
During 2015, Rindal Vinyards Inc. had Revenue of $1000, Depreciation and Amortization Expense of $100, Interest Expense of $100, and Tax Expense of $50. All other Expenses were $400. What was Rindal Vinyards’ EBITDA for 2015? 

```{r}
1000 + (100 + 100 + 50)
```
**EBITDA = 1000**


#### Incorrect

Net Income = Revenue - Expenses (COGS) - Interest Expense - Tax Expense - Deprec
Net Income = 1000 - 400 - 100 - 100 - 50 = 350

EBITDA = Net Income + Tax Expense + Interest Expense + Deprec
EBITDA = 350 + 50 + 100 + 100 = **600**


### Question 3
Geller Florist Inc. had the following transactions during 2015:

Purchased a $200,000 warehouse with $50,000 cash and a $150,000 mortgage from a bank.

Raised $100,000 from selling new shares of stock to investors. The cash was used to buy land to grow tulips.

Sold an old building for $50,000 (and suffered a loss on sale of $5,000) and used the cash to buy a new truck.

What is the net impact of these transactions on Geller's Cash from Financing Activities during 2015?

Transaction     | Cash      | Operating | Investing | Financing
---             | ---       | ---       | ---       | ---
Buy Bldg        | (50,000)  |           |           | 150,000
Sell Shares     | 100,000   |           |           | 100,000
Sell Bldg       |  50,000   |           | 50,000    |
Loss on sale    |  (5,000)  |           | (5,000)   |
Buy truck       |  50,000   |           | 50,000    |

**$250,000**


### Question 4

Stewart Export Co. had the following Statement of Cash Flows for the year ended 03/31/15:

($ millions) |	Year ended 3/31/15
 --- | --- 
Net Income |	1100
Depreciation |	200
Loss on sale of equipment |	400
Chg in Accounts Receivable |	350
Chg in Inventory |	(200)
Chg in Other Assets |	100
Chg in Accounts Payable |	(50)
Chg in Other Payables |	150
Net Cash from Operations |	2050
Capital Expenditures |	(1200)
Sale of Equipment | 	700
Net Cash from Investing |	(500)

What was the book value of the equipment Stewart sold during the year ended 03/31/15?  
**$700**

#### Incorrect

**$1,100** (700 + 400)


### Question 5
Little Scuba Pty had the following line item on its 12/31/2014 Balance Sheet:

Item    | 12/31/2014
---     | ---
Accounts Payable    |	$10,000

Little Scuba’s Statement of Cash Flows had the following line item:

Item    |	2014
---     | ---
Change in Accounts Payable  |	$4,000

Assume that the company made no acquisitions or divestitures and that all operations are in Australia. How much Accounts Payable did Little Scuba have on 12/31/2013?  
**$6,000**


### Question 6
A new accountant, Tia Count, put together a preliminary version of Medina Co.'s financial statements. Medina's Net Income was $500, its Depreciation Expense was $100, and its Cash Flow from Operations was $70. The CEO found an error that Tia made in computing straight-line Depreciation Expense, which should have been $150. What is Medina's Cash Flow from Operations after fixing this mistake? (you can ignore taxes)

Item    |   SCF
---     |   ---
Sales   |   650
COGS    |   (50)
Deprec  |   (100)
**NI**  |   500

Item        |   Direct SCF
---         |   ---
Collection  |   120
Payment     |   (50)
Operating Cash Flow     |   70

Item            |   Indirect SCF
---             |   ---
Net Income      |   500
Incr. in A/R    |   (650-120) = (530)
Depreciation Expense    |   100
Operating Cash Flow     |   70

**$70** Take out $150 in SCF, put back in $150 in Indirect SCF


### Question 7
Joe Doakes was reading the balance sheet of Gogoldze Inc. when he spilled coffee on it. After the coffee spill, the balance sheet looked like this:

($ millions)    |	12/13/2015
---             |   ---
Cash    |   100
Accounts Receivable    |	245
Inventory    |	450
Other Current Assets    |	60
Current Assets    |	855
Net Property, Plant, & Equipment    |	1,160
Total Assets    |	2,015
Accounts Payable    |	160
Other Current Liabilities    | 	250
Current Liabilities    | 	410
Long-term Liabilities    |	900
Common Stock    |	50
Additional Paid-in Capital    |	300
Retained Earnings    |	coffee
Total Liabilities and SE    |	coffee

What was Gogoldze Inc.'s Retained Earnings at 12/31/2015?

Total Assets = Liabilities + Stockholders' Equity

```{r}
assets <- 2015
liab <- 160 + 250 + 410 + 900

se <- assets - liab

re <- se - 50 - 300
re
```

#### Incorrect
```{r}
assets <- 2015
liab <- 410 + 900

se <- assets - liab

re <- se - 50 - 300
re
```
**$355**


### Question 8
Alejandro Alvera of Alvear Corp was reading the financial statements of Olivas Medical Supply Company to decide whether he wanted to try to acquire the company. He noticed some mistakes in the Olivas Income Statement:

($ millions)    |	Year ended 12/31/2015
---             |   ---
Sales revenue    |	$1600
Interest Revenue    |	50
Total Revenue    |	1650
Cost of Goods Sold    |	(800)
Gross Profit    |	850
SG&A Expense    |	(400)
Interest Expense    |	(50)
Operating Income    |	400
Gain on sale of equipment    |	200
Pre-tax income    |	600
Income Tax Expense    |	(216)
Net Income    |	384

What is Olivas' Operating Income for the year ended 12/31/2015 after correcting the mistakes?  
**$450** -- 'Interest Expense' comes after 'Operating Income'

#### Incorrect
